\documentclass[11pt,a4paper,english]{scrreprt}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[ansinew]{inputenc}


\usepackage{xcolor}
\usepackage{relsize}
\usepackage{paralist}
\usepackage{typearea}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{amsmath}
\usepackage{array}
\usepackage{booktabs}


%%%----------------------------------------------------------------------
\definecolor{dunkelgrau}{gray}{0.20}
\definecolor{hellgrau}{gray}{0.40}

\onehalfspacing
\typearea[current]{calc}

\newcommand{\changefont}[3]{
\fontfamily{#1} \fontseries{#2} \fontshape{#3} \selectfont}

\newcommand{\textemph}{\textsl{\textbf}}
%%%----------------------------------------------------------------------
\begin{document}

\begin{spacing}{1}

	\begin{titlepage}
		
		\begin{center}
		{\large Freie Universit\"{a}t Berlin\\
		Otto-Suhr\texttwelveudash
		Institut f\"{u}r Politikwissenschaft\\
		HS \\
		\emph{Projektkurs}\\
		\textsmaller{\textbf{Lecturers:} Prof. Miranda Schreurs \&
Dr. Helmut Weider}}\par
		
		\vspace{4cm}
		
\changefont{ppl}{b}{n}
\sffamily{
  {\Huge{\textsmaller{\textbf{Term Paper}}}\\
 \bigskip	 
 \textcolor{dunkelgrau}{EU Energy Policy: Security Of Natural Gas Supply}}}
		
\par

\vspace{4cm}
		
\changefont{lmr}{m}{n}
		
		{\large Pascal Bernhard\\
		Schwalbacher Stra{\ss}e 7\\
		12161 Berlin\\
		Matrikelnummer: 3753179\\
		pascal.bernhard@belug.de}
		
		
		
		\end{center}

	\end{titlepage}
	
\end{spacing}

%%%----------------------------------------------------------------------


%%%----------------------------------------------------------------------
\tableofcontents


%%%----------------------------------------------------------------------
\setlength{\parindent}{30pt}
\setlength{\parskip}{0pt}


%%%-----------------------------------------------------------------------

\chapter{Introduction}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Structure \& Research Question}
	




	\paragraph{Proceeding}


	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{SECOND CHAPTER}	
	

  \section{FIRST SECTION OF SECOND CHAPTER}
 
    \paragraph{A PARAGRAPH FOR SECTIONING}

  \section{SECOND SECTION OF SECOND CHAPTER}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{THIRD CHAPTER}



 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 
\chapter{FOURTH CHAPTER}





  \section{FIRST SECTION OF FOURTH CHAPTER}


  
  
\chapter{Conclusion}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{Sources}

  \begin{itemize}
	
	\sffamily
	
	\item [\Rectsteel] \textbf{Blom-Hansen, Jens (2008):} The Origins Of
The EU Comitology System: A Case Of Informal Agenda-Setting By The Commission,
in: \textsl{Journal of European Public Policy}, Vol. 15, Issue 2, p. 208-226.
	
	
	\item [\Rectsteel] \textbf{Franchino, Fabio (2000):} Control Of The
Commission's Executive Functions: Uncertainty, Conflict And Decision Rules
in: \textsl{European Union Politics}, Vol. 1, Issue 1, p. 63-92.


	\item [\Rectsteel] \textbf{Kiewiet, D. Roderick \& McCubbins, Mathew D.
(1991):} The Logic Of Delegation. Congressional Parties And The Appropriations
Process, Chicago.


	\item [\Rectsteel] \textbf{McCubbins, Mathew D. \& Page, Talbot
(1987):} A Theory Of Congressional Delegation in: McCubbins, Mathew
D. \& Sulliva, T. (eds) )\textsl{Congress: Structure And Policy}, p. 409-425,
Cambridge, MA, United States of America.
	
	
	\item [\Rectsteel] \textbf{Pollack, Mark A.(1997):} Delegation, Agency,
And Agenda Setting In The European Community, in: \textsl{International
Organization}, Vol. 51, p. 99-134.	

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
	\item [\Rectsteel] \textbf{NAME, SURNAME (AUTHOR I), NAME, SURNAME
(AUTHOR II)\& NAME, SURNAME (YEAR):} TITLE OF PAPER OR BOOK,
in: \textsl{TITLE OF JOURNAL}, Vol. ++, Issue ++, p. ++-++.


	\item [\Rectsteel] \textbf{NAME, SURNAME (AUTHOR I), NAME, SURNAME
(AUTHOR II)\& NAME, SURNAME (YEAR):} TITLE OF PAPER OR BOOK,
in: \textsl{NAME OF INSTITUTION OR RESEARCH OUTFIT (option)}, LOCATION OF
PUBLISHER.


  \end{itemize}




\end{document}